Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Scale Up Example.

\newpage
\begin{figure}[h]
$\begin{array}{r@{}l}
    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
    	   {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
\end{array}$
  \smallskip

@@

\newpage
\subsection{Scaling up: several subsystems on the same bus}

\TODO{Not yet !}

\end{document}

>>>>

\subsection{Scaling up: several subsystems on the same bus}
\TODO{Not yet !}
\begin{figure}
    \centerline{\includegraphics[width=\linewidth]{XFIG/ScaleUp}}
    \caption{pNet encoding of the composition of two Failure Monitoring modules}  \label{schema:scaleup}
\end{figure}

We build a larger system by composing several subsystems. In the example here, we use two Failure Monitoring modules as the subsystems.
To compose them, a new controller is added for managing the reset function of the whole system. 
No matter which module behaves an "ask" to call for reset, the controller take the request. Then all of the modules conduct the "reset".
So two more new transitions are added to the Timer to make the module can reset at any state.

There are 327 satisfiable results, out of totally 97920 results, of the example computed in 105384 milliseconds.

\newpage
\begin{figure}
$\begin{array}{r@{}l}
    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
    	   {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
\end{array}$
  \smallskip

@@

\newpage
\end{document}
